---
title: "Choosing features and metrics for nearest neighbor search"
author: "Varun Boodram"
date: "July 8, 2016"
output:
  html_document:
    theme: cerulean
  pdf_document: default
---

When exploring a large set of documents -- such as Wikipedia, news articles, StackOverflow, etc. -- it can be useful to get a list of related material. To find relevant documents you typically

* Decide on a notion of similarity
* Find the documents that are most similar

In the assignment you will

* Gain intuition for different notions of similarity and practice finding similar documents.
* Explore the tradeoffs with representing documents using raw word counts and TF-IDF
* Explore the behavior of different distance metrics by looking at the Wikipedia pages most similar to President Obama’s page.

```{r}
# loading the data
setwd("~/Desktop/Coursera-MLS-Clustering_and_Retrevial")
wiki <- read.csv2(file = unzip(
        "./datasets/people_wiki.csv.zip"),
                  header = T, 
                  sep = ",")
```

Next, we extract word count vectors

```{r}
require(tm)
train_corpus <- VCorpus(VectorSource(wiki$text))
train_matrix <- DocumentTermMatrix(train_corpus, 
                                   control = list(stopwords = FALSE,
                                                  wordLengths =c(1, Inf),
                                                  removePunctuation =T))
m <- removeSparseTerms(x = train_matrix, sparse = .999)
m2<-as.matrix(inspect(m))
tdm <- as.matrix(inspect(train_matrix))
```

